### 2021-11-27 documents/floats/ppekverbs.tex
new approach to testing predictions from bybee's model
some minor fixes, better PTar form for 'to go down'

\begin{table}
\centering
\caption[Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PPek]{Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PPek \parencites[153, 200]{alves2017arara}[76, 130, 131, 137, 374, 397]{von1892bakairi}[42, 80, 139, 209]{ikpengpacheco2001}[68]{ikpengpacheco1997}[4; p.c., Angela Fabíola Alves Chagas]{meira2003bakairi}}
\label{tab:ppekverbs}
\begin{tabular}[t]{@{}lllll@{}}
\mytoprule
{} &          \PPek &          \arara &                       \ikpeng &        \bakairi \\
\midrule
\qu{be-1}    &     \rc{w-ap-} &     \obj{w-ap-} &                             – &      \obj{w-a-} \\
\qu{be-2}    &  \rc{w-et͡ʃi-} &  \obj{w-it͡ʃi-} &  \obj{{\normalfont ∅}-et͡ʃi-} &      \obj{w-i-} \\
\qu{say}     &    \rc{wɨ-ge-} &    \obj{wɨ-ge-} &                   \obj{ɨ-ge-} &     \obj{u-ge-} \\
\qu{go}      &   \rc{w-ɨtən-} &    \obj{w-ɨdo-} &                 \obj{k-aran-} &     \obj{u-tə-} \\
\qu{come}    &    \rc{w-epɨ-} &    \obj{w-ebɨ-} &                 \obj{k-arep-} &   \obj{k-əewɨ-} \\
\qu{go down} &   \rc{w-ɨptə-} &  \obj{w-iptoŋ-} &  \obj{{\normalfont ?}-iptoŋ-} &  \obj{k-ɨtəgɨ-} \\
\qu{bathe}   &    \rc{w-ipɨ-} &    \obj{w-ibɨ-} &     \obj{{\normalfont ∅}-ip-} &      \obj{w-i-} \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PPek]{Verbs preserving \gl{1}\gl{s_a_} \rc{w-} in \PPek \parencites[153, 200]{alves2017arara}[76, 130, 131, 374, 397]{von1892bakairi}[42, 80, 139, 209]{ikpengpacheco2001}[68]{ikpengpacheco1997}[4]{meira2003bakairi}}
\label{tab:ppekverbs}
\begin{tabular}[t]{@{}lllll@{}}
\mytoprule
{} &          \PPek &          \arara &                       \ikpeng &       \bakairi \\
\mymidrule
\qu{be-1}    &     \rc{w-ap-} &     \obj{w-ap-} &                             – &     \obj{w-a-} \\
\qu{be-2}    &  \rc{w-et͡ʃi-} &  \obj{w-it͡ʃi-} &  \obj{{\normalfont ∅}-et͡ʃi-} &     \obj{w-i-} \\
\qu{say}     &    \rc{wɨ-ge-} &    \obj{wɨ-ge-} &                   \obj{ɨ-ge-} &    \obj{u-ge-} \\
\qu{go}      &   \rc{w-ɨtən-} &    \obj{w-ɨdo-} &                 \obj{k-aran-} &    \obj{u-tə-} \\
\qu{come}    &    \rc{w-epɨ-} &    \obj{w-ebɨ-} &                 \obj{k-arep-} &  \obj{k-əewɨ-} \\
\qu{go down} &   \rc{w-ɨptə-} &                 &                               &                \\
\qu{bathe}   &    \rc{w-ipɨ-} &    \obj{w-ibɨ-} &     \obj{{\normalfont ∅}-ip-} &     \obj{w-i-} \\
\mybottomrule
\end{tabular}
\end{table}

### 2021-11-27 documents/floats/pwaireg.tex
some minor fixes, better PTar form for 'to go down'

\begin{table}
\centering
\caption[Regular \PWai verbs]{Regular \qu{to fall} (\gl{s_a_}) and \qu{to sleep} (\gl{s_p_}) in \PWai \parencites[30]{waiwaihawkins1998}[189, 190, 196]{hixkaryanaderby1985}[150]{howard2001wrought}[209, 211]{hawkins1953waiwai}}
\label{tab:pwaireg}
\begin{tabular}[t]{@{}lllllll@{}}
\mytoprule
{} & \multicolumn{2}{l}{\PWai} & \multicolumn{2}{l}{\hixka} & \multicolumn{2}{l}{\waiwai} \\
{} &    \qu{to fall} &     \qu{to sleep} &     \qu{to fall} &   \qu{to sleep} &       \qu{to fall} &      \qu{to sleep} \\
\midrule
\gl{1}   &  \rc{k-eɸurka-} &   \rc{kɨ-wɨnɨkɨ-} &  \obj{k-ehurka-} &  \obj{kɨ-nɨkɨ-} &    \obj{k-eɸɨrka-} &   \obj{kɨ-wɨnɨkɨ-} \\
\gl{2}   &  \rc{m-eɸurka-} &    \rc{o-wɨnɨkɨ-} &  \obj{m-ehurka-} &  \obj{o-wnɨkɨ-} &    \obj{m-eɸɨrka-} &   \obj{mɨ-wɨnɨkɨ-} \\
\gl{1+2} &  \rc{t-eɸurka-} &  \rc{tɨt-wɨnɨkɨ-} &  \obj{t-ehurka-} &  \obj{tɨ-nɨkɨ-} &  \obj{t͡ʃ-eɸɨrka-} &  \obj{tɨt-wɨnɨkɨ-} \\
\gl{3}   &  \rc{ɲ-eɸurka-} &   \rc{nɨ-wɨnɨkɨ-} &  \obj{ɲ-ehurka-} &  \obj{nɨ-nɨkɨ-} &    \obj{ɲ-eɸɨrka-} &   \obj{nɨ-wɨnɨkɨ-} \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Regular \PWai verbs]{Regular \qu{to fall} (\gl{s_a_}) and \qu{to sleep} (\gl{s_p_}) in \PWai \parencites[30]{waiwaihawkins1998}[189, 190, 196]{hixkaryanaderby1985}[150]{howard2001wrought}[209, 211]{hawkins1953waiwai}}
\label{tab:pwaireg}
\begin{tabular}[t]{@{}lllllll@{}}
\mytoprule
{} &           \PWai &                   &           \hixka &                 &            \waiwai &                    \\
{} &    \qu{to fall} &     \qu{to sleep} &     \qu{to fall} &   \qu{to sleep} &       \qu{to fall} &      \qu{to sleep} \\
\mymidrule
\gl{1}   &  \rc{k-eɸurka-} &   \rc{kɨ-wɨnɨkɨ-} &  \obj{k-ehurka-} &  \obj{kɨ-nɨkɨ-} &    \obj{k-eɸɨrka-} &   \obj{kɨ-wɨnɨkɨ-} \\
\gl{2}   &  \rc{m-eɸurka-} &    \rc{o-wɨnɨkɨ-} &  \obj{m-ehurka-} &  \obj{o-wnɨkɨ-} &    \obj{m-eɸɨrka-} &   \obj{mɨ-wɨnɨkɨ-} \\
\gl{1+2} &  \rc{t-eɸurka-} &  \rc{tɨt-wɨnɨkɨ-} &  \obj{t-ehurka-} &  \obj{tɨ-nɨkɨ-} &  \obj{t͡ʃ-eɸɨrka-} &  \obj{tɨt-wɨnɨkɨ-} \\
\gl{3}   &  \rc{ɲ-eɸurka-} &   \rc{nɨ-wɨnɨkɨ-} &  \obj{ɲ-ehurka-} &  \obj{nɨ-nɨkɨ-} &    \obj{ɲ-eɸɨrka-} &   \obj{nɨ-wɨnɨkɨ-} \\
\mybottomrule
\end{tabular}
\end{table}
